%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {MyTi Technetronics Pvt. Ltd.} % Organization
    {Founder-CEO, R \& D Chief} % Job title
    {New Delhi/Pilani} % Location
    {Dec, 2012 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked on building an R \& D company in design and electronics.}
        \item {Developed MyTi.Note tablet, Zappowr \& did consulting for research projects.}
        \item {Did product design, component selection, prototyping, testing etc.}
        \item {Acquired various skills ranging from embedded systems design to final PCB design, technology research to firmware coding}
      \end{cvitems}
    }

    \cventry
    {Department of Physics \& Astrophysics, University of Delhi} % Institution
    {Research Scholar} % Degree
    {Delhi} % Location
    {Feb, 2012 - PRESENT} % Date(s)
    {
    \begin{cvitems} 
      %\item {Trying to make sense of the cosmos using some exotic models of the Universe for Ph. D. in Cosmology}
      \item {Currently preparing thesis on alternative models of gravity and Cosmology for Ph.D. in Physics.}
    \end{cvitems}
    }
    
    %---------------------------------------------------------
  \cventry
    {Shridhar University} % Organization
    {Assistant Professor} % Job title
    {Pilani} % Location
    {Aug, 2015 - Aug, 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Taught Embedded Systems and Programming, Optical Communication \& Fiber Optics, Basic Physics to B.E. (Electronics) students.}
        \item {Helped setup Robotics lab and Astronomy club along with guiding student projects.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {SGTB Khalsa College, University of Delhi} % Organization
    {Guest Lecturer} % Job title
    {New Delhi} % Location
    {Aug, 2011 - Mar, 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Taught Electromagnetic Theory, Signals \& Systems, C++ Programming to B.Sc (Electronics) students.}
        \item {Conducted lab practicals along with guiding student projects.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {GITAM University} % Organization
    {Guest Lecturer} % Job title
    {Visakhapatnam, Andhra Pradesh} % Location
    {Sept, 2010 - May, 2011} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Taught core courses to M.Sc (Electronics) and M.Sc (Physics) students along with projects.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {TutorVista Global Pvt Ltd, Pearson Education} % Organization
    {Tutor, College grade} % Job title
    {Online} % Location
    {Sep, 2010 - May, 2011} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Did online tutoring (teaching Physics) for college grade students.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {BITS-Pilani} % Organization
    {Teaching Assistant} % Job title
    {Pilani, Rajasthan} % Location
    {Aug, 2009 - Feb, 2010} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Helped in setting up Wireless Communications Lab.}
        \item {Worked as TA for Electronic Devices \& Integrated Circuits, Digital Electronics \& Microprocessor Programming and Measurement Techniques courses.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {STMicroelectronics} % Organization
    {Intern, Tech R \& D Group} % Job title
    {Greater Noida, Uttar Pradesh} % Location
    {Jul, 2008 - Jun, 2009} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a “High Speed Transceiver High Precision SILICON-CAD Validation Methodology Development” which is aimed at designing a new flow for signal integrity verification.}
        \item {Did a semi-custom design of an “All Digital Phase-Locked Loop” for digitally controlled clock generation using the standard cell libraries in CMOS090.}
        \item {Played an active role as a member of team consisted of 8 members in verification of a chip named Bolero in Automotive Product Group.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
