%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Industry/Startup Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

\cventry
{LightSpeedAI Labs Pvt. Ltd.} % Organization
{Chief Technology Officer} % Job title
{Bengaluru} % Location
{Mar, 2019 - Present} % Date(s)
{
	\begin{cvitems} % Description(s) of tasks/responsibilities
		\item {Building opto-electronic processors for accelerating Machine Learning/Artificial Intelligence applications}
	\end{cvitems}
}

\cventry
{Entrepreneur First} % Organization
{Founder-in-Residence} % Job title
{Bengaluru} % Location
{Feb, 2019 - Present} % Date(s)
{
	\begin{cvitems} % Description(s) of tasks/responsibilities
		\item {Fellowship \& Pre-seed raised from Entrepreneur First}
	\end{cvitems}
}

%---------------------------------------------------------
\cventry
{IoTfy Inc.} % Organization
{Consulting Engineer, Hardware} % Job title
{New Delhi} % Location
{Dec, 2016 - May, 2018} % Date(s)
{
	\begin{cvitems} % Description(s) of tasks/responsibilities
		\item {Built and wrote firmware for Smart RO systems with IoT integration}
		\item {Calibrated TDS sensors for Water purity testing}
	\end{cvitems}
}
%---------------------------------------------------------

%---------------------------------------------------------
  \cventry
    {MyTi Technetronics Pvt. Ltd.} % Organization
    {Founder-CEO, R \& D Chief} % Job title
    {New Delhi/Pilani} % Location
    {Dec, 2012 - May, 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked on building an R \& D company in design and electronics.}
        \item {Developed MyTi.Note tablet, Zappowr \& did consulting for research projects.}
        \item {Did product design, component selection, prototyping, testing etc.}
        \item {Acquired various skills ranging from embedded systems design to final PCB design, technology research to firmware coding}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {STMicroelectronics} % Organization
    {Intern, Tech R \& D Group} % Job title
    {Greater Noida, Uttar Pradesh} % Location
    {Jul, 2008 - Jun, 2009} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a “High Speed Transceiver High Precision SILICON-CAD Validation Methodology Development” which is aimed at designing a new flow for signal integrity verification.}
        \item {Did a semi-custom design of an “All Digital Phase-Locked Loop” for digitally controlled clock generation using 90nm node standard cell libraries.}
        \item {Played an active role as a member of team consisted of 8 members in verification of a chip named Bolero in Automotive Product Group.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
